Key Derivation From Noisy Sources With More Errors Than Entropy

### 2014-09-30 trunk/constantRate/ConstCompFuzzExt-reorg.tex
minor rewording of abstract/intro

\title{Key Derivation From Noisy Sources With More Errors Than Entropy}
%\author{Ran Canetti \and Benjamin Fuller \and Omer Paneth \and Leonid Reyzin \and Adam Smith}
\blind{
\author{Ran Canetti\footnote{Email: {\tt canetti@cs.bu.edu}. Boston University and Tel Aviv University.} \and Benjamin Fuller\footnote{Email: {\tt bfuller@cs.bu.edu}.  Boston University and MIT Lincoln Laboratory.} \and Omer Paneth\footnote{Email: {\tt paneth@cs.bu.edu}. Boston University.} \and Leonid Reyzin\footnote{Email: {\tt reyzin@cs.bu.edu}.  Boston University.} \and Adam Smith\footnote{Email: {\tt asmith@cse.psu.edu}.  Pennsylvania State University.} }
}
\begin{document}
\maketitle

\begin{abstract}
\lnote{needs work}
Fuzzy extractors convert a noisy source of entropy into the same uniformly distributed key~(Dodis et al., Eurocrypt 2004).  In the process of eliminating noise, they  lose some of the entropy of the original source---in the worst case, as much as the logarithm of the number of tolerated error patterns. For many practical sources, the error tolerance necessary to achieve reliable key derivation is larger than the entropy of the source.  Unfortunately, it is impossible to provide security for every source with this property.  Most known approaches for building fuzzy extractors work in the worst case and thus cannot be used when a source has \emph{more errors than entropy}.

Fortunately, practical sources contain useful structure.  In this work, we exploit distributional structure to construct fuzzy extractors for large classes of noisy sources with more errors than entropy.  
We show an information-theoretic construction and two computational constructions with added features.  Our constructions are for the Hamming metric over symbols of an alphabet.

\begin{itemize} \item \textbf{Information-theoretic}  Our first construction supports sources where each symbol contributes fresh entropy and corrects a constant fraction of Hamming errors over a super-constant size alphabet.

\item \textbf{Computational}
%By adding computational techniques we obtain constructions with additional features.  
Our second construction is also secure when each symbol contributes fresh entropy.  
Additionally, it is a reusable fuzzy extractor~(Boyen, CCS 2004).  A reusable fuzzy extractor allows multiple readings of the source to be enrolled securely.  Our construction is reusable if each individual reading is a supported source.  Previous reusable fuzzy extractors required the correlation between repeated readings to be drawn from a small and unrealistic class.  This construction corrects a sub-constant fraction of errors.  %Computational techniques allow us to show a very sshows that computational assu computationaprovide requires a constant fraction of symbols to have a constant amount of entropy conditioned on prior symbols. It corrects a sub-constant fraction of errors and supports super-constant size alphabets.  In addition, it is first construction of a reusable fuzzy extractor without assumption on the form of errors that occurs between reuse.  This is impossible in the information-theoretic setting for an arbitrary number of reuses~(Boyen, CCS 2004).

@@

\paragraph{Fuzzy Extractors}
Cryptography relies on long-term secrets for key derivation and authentication. However, many sources with sufficient randomness to form long-term secrets provide similar but not identical values at repeated readings~(prominent examples include biometrics and other human-generated data~\cite{daugman2004,zviran1993comparison,brostoff2000passfaces,ellison2000protecting,mayrhofer2009shake,monrose2002password},
physically unclonable functions (PUFs)~\cite{pappu2002physical,tuyls2006puf,gassend2002silicon,suh2007physical},
and quantum information~\cite{bennett1988privacy}). Turning similar readings into identical values is known as \emph{information reconciliation}; further converting those values into uniformly random secret strings is known as \emph{privacy amplification}~\cite{bennett1988privacy}.
Both of these problems have interactive and non-interactive versions.  In this paper, we are interested in the non-interactive case, which is useful for a single user trying to produce the same key from multiple readings of a physical source at different times.
 A \emph{fuzzy extractor} is the primitive that accomplishes both information reconciliation and privacy amplification non-interactively; fuzzy extractors are defined information-theoretically in~\cite{DBLP:journals/siamcomp/DodisORS08}.

Fuzzy extractors consist of a pair of algorithms: \gen (used once, at ``enrollment'') takes a source value $w$, and produces a key $r$ and a public helper value $p$.  The second algorithm \rep (used subsequently) takes this helper value $p$ and a close $w'$ to reproduce the original key $r$.
The correctness guarantee is that $r$ will be correctly reproduced by \rep as long as $w'$ is no farther than $t$ from $w$ in some metric space.% (in this paper, we focus on the Hamming metric on length $\gamma$ strings over some alphabet $\mathcal{Z}$). \onote{parameters $\gamma$ and $\mathcal{Z}$ are not used until they are reintroduced in our contribution paragraph. Consider ignoring them here.}
 The security guarantee is that $r$ produced by \gen is close to uniform (information-theoretically \cite{DBLP:journals/siamcomp/DodisORS08} or computationally \cite{fuller2013computational}), even given $p$. This guarantee holds as long as $w$ comes from a high-quality distribution, which
traditionally has been defined as \emph{any} distribution with sufficient min-entropy $m$.

@@

\begin{table}
\begin{tabular}{l l l c c}
 & Security & Source Structure & Error-Tolerance & Alphabet Size\\
\hline
\consref{cons:info theoretic} & Info-theoretic  & Partial block source& $\Theta(\gamma)$ & $\omega(1)$ \\
\consref{cons:sampling} & Reusable Computational & Partial block source& $o(\gamma)$ & $\omega(1)$ \\
\consref{cons:first construction} & Computational & Unguessable block source & $\Theta(\gamma)$ & $n^{\omega(1)}$
\end{tabular}
\caption{Summary of new constructions.  All constructions support families of distributions with more errors than entropy.  Partial blocks sources are defined in \defref{def:partial source} and unguessable block sources are defined in \defref{def:block guessable}.}
\label{tab:upper bounds}
\end{table}

@@

We emphasize that the obfuscation techniques we use are much weaker than general obfuscation, and can be instantiated quite efficiently under appropriate assumptions.

\paragraph{Connection to General Obfuscation}
We note that fuzzy extractors for sources with more errors than entropy can be trivially constructed from virtual grey-box obfuscation for the class of {\em proximity point programs}. A proximity point program $I_w(x)$ tests if $x$ is within distance $t$ of $w$. 
Recently, Bitansky et al.~\cite{BitanskyCKP14} constructed such obfuscation based on the strong assumption of {\em semantically secure graded encodings} \cite{PassTS13}.
The construction of Bitansky et al. is based on multilinear encoding and is  highly impractical.  The obfuscation used in this work can be instantiated quite efficiently under appropriate assumptions.
Additionally, the known obfuscation for proximity point programs is not known to be composable and therefore does not yield a reusable fuzzy extractor.

@@

%\paragraph{Previous Negative Results}

%\bnote{old stuff}
%Their construction is secure when the correlations between $w_1,.., w_q$ come from a subgroup of permutations used in the construction of the fuzzy extractor.  They then show information-theoretic fuzzy extractors secure with unbounded reuse can be transformed into their construction~\cite[Theorem 11]{Boyen2004}.  This shows that correlation between $w_1,..., w_q$ must be restricted to this limited class.  There is no reason to expect that noise between repeated readings comes from a well-behaved subgroup of permutations.  Their result can be interpreted as saying that reusability is impractical.
%
%However, this result is inherently information-theoretic, the adversary must exhaust all randomness of the fuzzy extractor and computes statistical distance over exponential size strings.  There are two  restrictions to avoid this result: 1) limit the number of reuses of the fuzzy extractor 2) provide security against computational adversaries.  The second restriction implies the adversary will only observe a polynomial number of invocations of the fuzzy extractor.

%To overcome this result, we consider computationally bounded adversaries.
%We present a non-adaptive definition and note that our results extend to the adaptive definition presented by Boyen~\cite[Definition 7]{Boyen2004}.\bnote{We need to come back to justifying this or provide a proof that our scheme works in the adaptive setting.}
%\begin{definition}[Insider Reusable Fuzzy Extractors]
%\label{def:reusable fuzz}
%Let $\mathcal{W}$ be a family of distributions over $\mathcal{M}$.  Let $(\gen, \rep)$ be a $(\mathcal{M}, \mathcal{W}, \kappa, t)$-computational fuzzy extractor that is $(\epsilon, s)$-hard with error $\delta$.  Let $W_1,..., W_q$ be a joint distribution such that $\forall i, W_i\in\mathcal{W}$.  Let $(R_i, P_i)$ be the distribution formed by running $\gen$ on the distribution $W_i$.  We say that $(\gen, \rep)$ is $q$-reusable if for all $i$
%\begin{align*}
%\delta^{\mathcal{D}_{s}}(&(R_1, P_1), ..., (R_i, P_i),..., (R_q, P_q), \\
%&(R_1, P_1),..., (U_\kappa, P_i),..., (R_q, P_q)) < \epsilon.
%\end{align*}
%\end{definition}
We modify the definition of Boyen~\cite[Definition 6]{Boyen2004} for the computational setting.  We discuss the our definition and definitions due to Boyen in \apref{sec:comparing reusability}.

\begin{definition}[Reusable Fuzzy Extractors]
\label{def:outsider fuzz ext}
Let $\mathcal{W}$ be a family of distributions over $\mathcal{M}$.  Let $(\gen, \rep)$ be a $(\mathcal{M}, \mathcal{W}, \kappa, t)$-computational fuzzy extractor that is $(\epsilon, s)$-hard with error $\delta$.
Fix some $W_1 \in \mathcal{W}$.  Let $f_2,.., f_q , D$ be a split adversary.  Define the following game for all $i=1,..., q$:
\begin{itemize}%[leftmargin=-.6in]
\item \textbf{Sampling} The challenger samples $w_1\leftarrow W_1$.
\item \textbf{Perturbation} For $i=2,..., q$: the challenger computes $(r_i, p_i)\leftarrow \gen(w_i)$.  Set $w_{i+1} = f_i(w_1, p_1,..., p_i)$.\bnote{should we allow keys to the perturbation adversary?}
\item \textbf{Distinguishing} The advantage of $D$ is
\begin{align*}
\text{Adv}(D)&\overset{def}= \Pr[D(r_1,..., r_{i-1}, r_i, r_{i+1},..., r_q, p_1,..., p_q)=1]\\ &- \Pr[D(r_1,..., r_{i-1}, u, r_{i+1},..., r_q, p_1,..., p_q)=1].
\end{align*}
where $u$ is a uniformly random string.
\end{itemize}
$(\gen, \rep)$ is $(q, s_{sec}, \epsilon_{sec}, f_2,..., f_q)$-reusable if for all $D\in\mathcal{D}_{s_{sec}}$ the advantage is at most $\epsilon_{sec}$.
\end{definition}

@@

\begin{definition}
Let $(\gen, \rep)$ be a $(\mathcal{M}, \mathcal{W}, \kappa, t)$-computational fuzzy extractor that is $(\epsilon, s)$-hard with error $\delta$.  In the reusability game above, we say a set of functions $f_2,..., f_q$ are \emph{admissible} if for all $W_1\in \mathcal{W}$ for all $w_1\in W_1$ and $\forall p_1,..., p_q$ that are the public outputs of $\gen$ the implicit distribution $W_{i,w_1,p_1,..., p_{i-1}} = f_i(w_1,p_1,..., p_{i-1})$ is a member of $\mathcal{W}$.
\end{definition}

@@

In this section we show that \consref{cons:info theoretic} supports partial block sources with more errors than entropy.  The required entropy of partial block source is $\alpha (\gamma-\beta ) = \Theta(\gamma)$.  The condenser of Dodis et al~\cite{dodis2014key} has a constant entropy loss, so $\alpha-\tilde{\alpha} = \Theta(1)$. This means that the input entropy to the fuzzy extractor is $\Theta(\gamma)$.   We assume that the new alphabet $\mathcal{Y}$ is of constant size.  Standard fuzzy extractors on constant size alphabets correct a constant fraction of errors at a entropy loss of $\Theta(\gamma)$, yielding $\kappa = \Theta(\gamma)$.  Thus, our construction is secure for distributions with more errors than entropy whenever $|\mathcal{Z}| = \omega(1)$.
More formally:
\[
\text{\# Errors} - \text{Entropy} = \log |B_t| - \Hoo(W) <  t \log |\mathcal{Z}| - \Theta(\gamma)-= \Theta(\gamma) \log |\mathcal{Z}| - \Theta(\gamma)  > 0
\]
That is, there exists a super-constant alphabet size for which \consref{cons:info theoretic} is secure with more errors than entropy.

@@

\begin{center}
\begin{tabular}{c|c}
\begin{minipage}{3in}
\textbf{\gen}
\begin{enumerate}
\item \underline{Input}: $w = w_1,..., w_\gamma$
\item Sample $r \overset{\$}\leftarrow \zo^\kappa$.
\item For $i=1,..., \ell$:
\begin{enumerate}[(i)]
\item Select $\lambda_i\overset{\$}\leftarrow \zo^{r_{sam}}$.
\item Set $j_{i, 1},..., j_{i, \eta}\leftarrow \sample_{\eta,\gamma}( \lambda_i)$
\item Set $v_i = w_{j_{i,1}},..., w_{j_{i, \eta}}$.
\item Set $\rho_i = \mathcal{O}(I_{v_i, r})$.
\item Set $p_i = \rho_i, \lambda_i$.
\end{enumerate}
\item Output $(r, p)$, where $p=p_1\dots p_\ell$.
\end{enumerate}
 \end{minipage} &
\begin{minipage}{3in}
\textbf{\rep}
\begin{enumerate}
\item \underline{Input}: $(w', p)$
\item For $i=1,..., \ell$:
\begin{enumerate}[(i)]
\item Parse $p_i$ as $\rho_i, \lambda_i$.
\item Set $j_{i, 1},..., j_{i, \eta}\leftarrow \sample_{\gamma, \eta}(\lambda_i)$.
\item Set $v_i' = w_{j_{i, 1}},..., w_{j_{i, \eta}}$.
\item Set $\rho_i(v_i') = r_i$.  If $r_i\neq \perp$ output $r_i$.
\end{enumerate}
\item Output $\perp$.
\end{enumerate}
\vspace{0.37in}
\end{minipage}
\end{tabular}
\end{center}
\end{construction}

\noindent
%There are three main differences between this construction and \consref{cons:first construction}.  They are as follows:
%\begin{itemize}
%\item Multiple blocks are concatenated together.  This comes at a cost to error tolerance but allows us to significant decrease the required entropy in each block.  This paradigm is similar to \emph{sample-then-extract} from the locally computable extractors literature~\cite{lu2002hyper,vadhan2003constructing}.  For this reason we call \consref{cons:sampling} \emph{sample-then-obfuscate}.
%\item Instead of encoding a bit of the key with each obfuscated value we encode the entire key with each obfuscated value.  This requires the use of digital lockers in place of point obfuscations.  Instead of having to open ``most'' of the obfuscations, it is only necessary for us to open a single obfuscation.  \consref{cons:first construction} only hid part of the key in each obfuscation.  This allowed some blocks in the distribution to be ``weak.''  However, sampling smoothes out $W$ so that all $V_i$ are ``good'' simultaneously.
%\item \consref{cons:first construction} required a large alphabet as blocks were individually obfuscated.  This construction works for an arbitrary size alphabet.  We show it supports $\Huse (W)\le 0$ when the alphabet size is super-constant in the security parameter.
%\end{itemize}
The use of a computational primitive~(obfuscation) allows us to sample multiple times, because we need to argue only about individual entropy of $V_i$, as opposed to the information-theoretic setting, where it would be necessary to argue about the entropy of the joint variable $V$.  This is the property that allows reusability.

This construction uses a na\"{i}ve sampler that takes truly random samples, but the public randomness may be substantially decreased by using more sophisticated samplers. Goldreich provides an introduction to samplers in~\cite{goldreich2011sample}.

@@

\begin{theorem}
\label{thm:reusability}
Let $q = \poly(n)$, and let all the variables be as in \thref{thm:sampling}, except that $\mathcal{O}$ be an $\ell\times q$-composable VGB obfuscator for digital lockers~(with $\kappa$ bit outputs) with auxiliary inputs.  For any admissible $f_2,..., f_q$, for all $s_{sec} = \poly(n)$ there exists some $\epsilon_{sec} = \ngl(n)$ such that $(\gen, \rep)$ is $(q, s_{sec}, \epsilon_{sec}, f_2,..., f_q)$-reusable fuzzy extractor.
\end{theorem}
\begin{proof}
The only modification to the outline presented in \secref{ssec:sec cons sampling} is in \lemref{lem:samp unguess} with the other keys $R_1,..., R_{i-1}, R_{i+1}, ..., R_q$ treated as additional auxiliary input to the adversary/simulator.  The simulator in the definition of composable obfuscation is required to function for arbitrary circuits in the family even if the choice of these circuits depends on the previous obfuscations.
\bnote{say more here?}
\end{proof}

\subsection{More errors than entropy?}
In this section, we show when \consref{cons:sampling} supports partial block sources with more errors than entropy.  The required entropy of partial block source is $\alpha (\gamma-\beta ) = \Theta(\gamma)$.  We are able to correct $o(\gamma)$ errors.
This yields:
\[
\text{\# Errors} - \text{Entropy} =  \log |B_t| -\Hoo(W) < t \log |\mathcal{Z}| - \Theta(\gamma)= o(\gamma) \log |\mathcal{Z}| - \Theta(\gamma)
\]
That is, there exists a super-constant alphabet size for which \consref{cons:sampling} is secure with more errors than entropy.  We note that \consref{cons:sampling} works for an arbitrary size alphabet; however, for a constant size alphabet, the required entropy is greater than the number of corrected error patterns.  However, \consref{cons:sampling} is reusability for an arbitrary size alphabet.

\section{Allowing Correlated Symbols}
\label{sec:cor construction}
In the previous two sections, we presented constructions that supported restricted classes of distributions with more errors than entropy.  Unfortunately, both Constructions~\ref{cons:info theoretic} and \ref{cons:sampling} required each symbol to contribute ``fresh'' entropy.  In this section, we present a computational construction that allows for correlation between symbols while still supporting more errors than entropy and correcting a constant fraction of errors.
This construction is inspired by the construction of digital lockers from point obfuscation by Canetti and Dakdouk~\cite{canetti2008obfuscating}.

>>>>

\title{Key Derivation From Noisy Sources With More Errors Than Entropy}
%\author{Ran Canetti \and Benjamin Fuller \and Omer Paneth \and Leonid Reyzin \and Adam Smith}
\blind{
\author{Ran Canetti\footnote{Email: {\tt canetti@cs.bu.edu}. Boston University and Tel Aviv University.} \and Benjamin Fuller\footnote{Email: {\tt bfuller@cs.bu.edu}.  Boston University and MIT Lincoln Laboratory.} \and Omer Paneth\footnote{Email: {\tt paneth@cs.bu.edu}. Boston University.} \and Leonid Reyzin\footnote{Email: {\tt reyzin@cs.bu.edu}.  Boston University.} \and Adam Smith\footnote{Email: {\tt asmith@cse.psu.edu}.  Pennsylvania State University; work performed while at Boston University's Hariri Institute for Computing and RISCS Center, and Harvard University's
``Privacy Tools'' project.} }
}
\begin{document}
\maketitle

\begin{abstract}
Fuzzy extractors (Dodis et al., Eurocrypt 2004) convert repeated noisy readings of a high-entropy secret into the same uniformly distributed key. To eliminate noise, they require an initial enrollment phase that takes the first noisy reading of the secret and produces a nonsecret helper string to be used in subsequent readings. This helper string reduces  the entropy of the original secret---in the worst case, by as much as the logarithm of the number of tolerated error patterns. For many practical sources of secrets, reliability demands that the number of tolerated error patterns is large, making this loss greater than the original entropy of the secret. We say that such sources have \emph{more errors than entropy}.  Most known approaches for building fuzzy extractors cannot be used for such sources.

%\emph{Reusable} fuzzy extractors (Boyen, CCS 2004)
% remain secure even when the initial enrollment phase is repeated multiple times on correlated readings, producing multiple helper strings. Prior approaches to building reusable fuzzy extractors severely restricted allowed correlations among initial enrollment readings.
%   
%We provide constructions of fuzzy extractors for large classes of sources with more errors than entropy.  We also construct the first reusable fuzzy extractors that has no restrictions on correlations among multiple readings of the source. Our constructions exploit the structural properties of a source in addition to its entropy guarantees. One is information-theoretic; the other two rely computational assumptions. They differ in the types of sources they support.

We provide constructions of fuzzy extractors for large classes of sources with more errors than entropy.  Our constructions exploit the structural properties of a source in addition to its entropy guarantees. Some are made possible by relaxing the security requirement from information-theoretic to computational.

%One is information-theoretic; the other two rely computational assumptions. They differ in the types of sources they support.

\emph{Reusable} fuzzy extractors (Boyen, CCS 2004)
 remain secure even when the initial enrollment phase is repeated multiple times with the same or correlated secrets, producing multiple helper strings. By relying on computational security, we construct the first reusable fuzzy extractors that make no assumption about how multiple readings of the source are correlated.

\iffalse

We construct fuzzy extractors for large classes of such sources by exploiting  their structural properties in addition to their entropy guarantees.  
We show an information-theoretic construction and two computational constructions with additional features.  Our constructions are for the Hamming metric over a nonbinary alphabet.

The information-theoretic construction supports sources in which most symbols contributes fresh entropy. The first computational construction has the additional feature of \emph{reusability}~(Boyen, CCS 2004), allowing multiple correlated

\begin{itemize} \item \textbf{Information-theoretic}  Our first construction supports sources where each symbol contributes fresh entropy and corrects a constant fraction of errors over a super constant size alphabet.

\item \textbf{Computational}
%By adding computational techniques we obtain constructions with additional features.  
Our second construction is also secure when each symbol contributes fresh entropy.  
Additionally, it is a reusable fuzzy extractor~(Boyen, CCS 2004).  A reusable fuzzy extractor allows multiple readings of the source to be enrolled securely.  Our construction is reusable if each individual reading is a supported source.  Previous reusable fuzzy extractors required the correlation between repeated readings to be drawn from a small and unrealistic class.  This construction corrects a sub-constant fraction of errors over a super constant size alphabet.  %Computational techniques allow us to show a very sshows that computational assu computationaprovide requires a constant fraction of symbols to have a constant amount of entropy conditioned on prior symbols. It corrects a sub-constant fraction of errors and supports super-constant size alphabets.  In addition, it is first construction of a reusable fuzzy extractor without assumption on the form of errors that occurs between reuse.  This is impossible in the information-theoretic setting for an arbitrary number of reuses~(Boyen, CCS 2004).

@@

\paragraph{Fuzzy Extractors}
Cryptography relies on long-term secrets for key derivation and authentication. However, many sources with sufficient randomness to form long-term secrets provide similar but not identical values at repeated readings. Prominent examples include biometrics and other human-generated data~\cite{daugman2004,zviran1993comparison,brostoff2000passfaces,ellison2000protecting,mayrhofer2009shake,monrose2002password},
physically unclonable functions (PUFs)~\cite{pappu2002physical,tuyls2006puf,gassend2002silicon,suh2007physical},
and quantum information~\cite{bennett1988privacy}. Turning similar readings into identical values is known as \emph{information reconciliation}; further converting those values into uniformly random secret strings is known as \emph{privacy amplification}~\cite{bennett1988privacy}.
Both of these problems have interactive and non-interactive versions.  In this paper, we are interested in the non-interactive case, which is useful for a single user trying to produce the same key from multiple noisy readings of a secret at different times.
 A \emph{fuzzy extractor} is the primitive that accomplishes both information reconciliation and privacy amplification non-interactively; fuzzy extractors are defined in~\cite{DBLP:journals/siamcomp/DodisORS08}.

Fuzzy extractors consist of a pair of algorithms: \gen (used once, at ``enrollment'') takes a source value $w$, and produces a key $r$ and a public helper value $p$.  The second algorithm \rep (used subsequently) takes this helper value $p$ and a close $w'$ to reproduce the original key $r$.
The correctness guarantee is that $r$ will be correctly reproduced by \rep as long as $w'$ is no farther than $t$ from $w$ in some metric space. In this work, we consider the Hamming metric.
 The security guarantee is that $r$ produced by \gen is close to uniform (information-theoretically \cite{DBLP:journals/siamcomp/DodisORS08} or computationally \cite{fuller2013computational}), even given $p$. This guarantee holds as long as $w$ comes from a high-quality distribution, which
traditionally has been defined as \emph{any} distribution with sufficient min-entropy $m$.

@@

\begin{table}
\begin{center}
\begin{tabular}{l l l l l}
 & Security & Source Structure & Error-Tolerance & Alphabet Size\\
\hline
Cons. \ref{cons:info theoretic} & Not reusable  & Most symbols  & Constant fraction & Super constant \\
&  Info-theoretic & contribute entropy & &\\\hline
Cons. \ref{cons:sampling} & Reusable & Most symbols & Sub constant fraction & Super constant \\
& Computational & contribute entropy & &\\\hline
Cons. \ref{cons:first construction} & Not reusable & Symbols correlated  & Constant fraction & Super polynomial\\
&  Computational & but hard to guess && 
\end{tabular}
\end{center}
%end centering
\caption{Summary of new constructions.  All constructions support families of distributions with more errors than entropy.}
\label{tab:upper bounds}
\end{table}

@@

\paragraph{Connection to General Obfuscation}
We note that fuzzy extractors for sources with more errors than entropy can be trivially constructed from virtual grey-box obfuscation for the class of {\em proximity point programs}. A proximity point program $I_w(x)$ tests if $x$ is within distance $t$ of $w$. 
Recently, Bitansky et al.~\cite{BitanskyCKP14} constructed such obfuscation based on the strong assumption of {\em semantically secure graded encodings} \cite{PassTS13}.
The construction of Bitansky et al. is based on multilinear encoding and is  highly impractical.  Our constructions use obfuscated digital lockers.  Obfuscated digital lockers are instantiable under significantly weaker assumptions and can be implemented quite efficiently.
\bnote{we need to say we are weaker than general obfuscation.  happy with this? merged with sentence from above}
Additionally, the known obfuscation for proximity point programs is not known to be composable and therefore does not yield a reusable fuzzy extractor.

@@

We modify the definition of Boyen~\cite[Definition 6]{Boyen2004} for the computational setting.  We discuss the our definition and definitions due to Boyen in \apref{sec:comparing reusability}.

\begin{definition}[Reusable Fuzzy Extractors]
\label{def:outsider fuzz ext}
Let $\mathcal{W}$ be a family of distributions over $\mathcal{M}$.  Let $(\gen, \rep)$ be a $(\mathcal{M}, \mathcal{W}, \kappa, t)$-computational fuzzy extractor that is $(\epsilon_{sec}, s_{sec})$-hard with error $\delta$.
Fix some $W_1 \in \mathcal{W}$.  Let $f_2,.., f_q , D$ be a split adversary.  Define the following game for all $j=1,..., q$:
\begin{itemize}%[leftmargin=-.6in]
\item \textbf{Sampling} The challenger samples $w_1\leftarrow W_1, u\leftarrow \zo^\kappa$.
\item \textbf{Perturbation} For $i=2,..., q$: the challenger computes $(r_i, p_i)\leftarrow \gen(w_i)$.  Set $w_{i+1} = f_i(w_1, p_1,..., p_i)$.\bnote{should we allow keys to the perturbation adversary?}
\item \textbf{Distinguishing} The advantage of $D$ is
\begin{align*}
\text{Adv}(D)&\overset{def}= \Pr[D(r_1,..., r_{j-1}, r_j, r_{j+1},..., r_q, p_1,..., p_q)=1]\\ &- \Pr[D(r_1,..., r_{j-1}, u, r_{j+1},..., r_q, p_1,..., p_q)=1].
\end{align*}
\end{itemize}
$(\gen, \rep)$ is $(q, \epsilon_{sec}, s_{sec}, f_2,..., f_q)$-reusable if for all $D\in\mathcal{D}_{s_{sec}}$ the advantage is at most $\epsilon_{sec}$.
\end{definition}

@@

\begin{definition}
Let $(\gen, \rep)$ be a $(\mathcal{M}, \mathcal{W}, \kappa, t)$-computational fuzzy extractor that is $(\epsilon_{sec}, s_{sec})$-hard with error $\delta$.  In the reusability game above, we say a set of functions $f_2,..., f_q$ are \emph{admissible} if for all $W_1\in \mathcal{W}$ for all $w_1\in W_1$ and $\forall p_1,..., p_q$ that are the public outputs of $\gen$ the distribution $W_{i,w_1,p_1,..., p_{i-1}} = f_i(w_1,p_1,..., p_{i-1})$ is a member of $\mathcal{W}$.
\end{definition}

@@

In this section we show that \consref{cons:info theoretic} supports partial block sources with more errors than entropy.  The structure of a partial block source implies that  $\Hoo(W) \ge \alpha (\gamma-\beta ) = \Theta(\gamma)$.  We assume that $\Hoo(W) = \Theta(\gamma)$. The condenser of Dodis et al~\cite{dodis2014key} has a constant entropy loss, so $\alpha-\tilde{\alpha} = \Theta(1)$. This means that the input entropy to $(\gen', \rep')$ is $\Theta(\gamma)$.   We assume that the new alphabet $\mathcal{Y}$ is of constant size.  Standard fuzzy extractors on constant size alphabets correct a constant fraction of errors at a entropy loss of $\Theta(\gamma)$, yielding $\kappa = \Theta(\gamma)$.  Thus, our construction is secure for distributions with more errors than entropy whenever $|\mathcal{Z}| = \omega(1)$.
More formally:
\[
\text{\# Errors} - \text{Entropy} = \log |B_t| - \Hoo(W) \ge  t \log |\mathcal{Z}| - \Theta(\gamma)-= \Theta(\gamma) \log |\mathcal{Z}| - \Theta(\gamma)  > 0
\]
That is, there exists a super-constant alphabet size for which \consref{cons:info theoretic} is secure with more errors than entropy.

@@

\begin{center}
\begin{tabular}{c|c}
\begin{minipage}{3in}
\textbf{\gen}
\begin{enumerate}
\item \underline{Input}: $w = w_1,..., w_\gamma$
\item Sample $r \overset{\$}\leftarrow \zo^\kappa$.
\item For $i=1,..., \ell$:
\begin{enumerate}[(i)]
\item Select $\lambda_i\overset{\$}\leftarrow \zo^{r_{sam}}$.
\item Set $j_{i, 1},..., j_{i, \eta}\leftarrow \sample_{\gamma,\eta}( \lambda_i)$
\item Set $v_i = w_{j_{i,1}},..., w_{j_{i, \eta}}$.
\item Set $\rho_i = \mathcal{O}(I_{v_i, r})$.
\item Set $p_i = \rho_i, \lambda_i$.
\end{enumerate}
\item Output $(r, p)$, where $p=p_1\dots p_\ell$.
\end{enumerate}
 \end{minipage} &
\begin{minipage}{3in}
\textbf{\rep}
\begin{enumerate}
\item \underline{Input}: $(w', p)$
\item For $i=1,..., \ell$:
\begin{enumerate}[(i)]
\item Parse $p_i$ as $\rho_i, \lambda_i$.
\item Set $j_{i, 1},..., j_{i, \eta}\leftarrow \sample_{\gamma, \eta}(\lambda_i)$.
\item Set $v_i' = w_{j_{i, 1}},..., w_{j_{i, \eta}}$.
\item Set $\rho_i(v_i') = r_i$.  If $r_i\neq \perp$ output $r_i$.
\end{enumerate}
\item Output $\perp$.
\end{enumerate}
\vspace{0.37in}
\end{minipage}
\end{tabular}
\end{center}
\end{construction}

\noindent
%There are three main differences between this construction and \consref{cons:first construction}.  They are as follows:
%\begin{itemize}
%\item Multiple blocks are concatenated together.  This comes at a cost to error tolerance but allows us to significant decrease the required entropy in each block.  This paradigm is similar to \emph{sample-then-extract} from the locally computable extractors literature~\cite{lu2002hyper,vadhan2003constructing}.  For this reason we call \consref{cons:sampling} \emph{sample-then-obfuscate}.
%\item Instead of encoding a bit of the key with each obfuscated value we encode the entire key with each obfuscated value.  This requires the use of digital lockers in place of point obfuscations.  Instead of having to open ``most'' of the obfuscations, it is only necessary for us to open a single obfuscation.  \consref{cons:first construction} only hid part of the key in each obfuscation.  This allowed some blocks in the distribution to be ``weak.''  However, sampling smoothes out $W$ so that all $V_i$ are ``good'' simultaneously.
%\item \consref{cons:first construction} required a large alphabet as blocks were individually obfuscated.  This construction works for an arbitrary size alphabet.  We show it supports $\Huse (W)\le 0$ when the alphabet size is super-constant in the security parameter.
%\end{itemize}
The use of a computational primitive~(obfuscation of digital lockers) allows us to sample multiple times, because we need to argue only about individual entropy of $V_i$, as opposed to the information-theoretic setting, where it would be necessary to argue about the entropy of the joint variable $V$.  This is the property that allows reusability.

This construction uses a na\"{i}ve sampler that takes truly random samples, but the public randomness may be substantially decreased by using more sophisticated samplers. (See Goldreich~\cite{goldreich2011sample} for an introduction to samplers.)

@@

\begin{theorem}
\label{thm:reusability}
Let $q = \poly(n)$, and let all the variables be as in \thref{thm:sampling}, except that $\mathcal{O}$ be an $\ell\times q$-composable VGB obfuscator for digital lockers~(with $\kappa$ bit outputs) with auxiliary inputs.  For any admissible $f_2,..., f_q$, for all $s_{sec} = \poly(n)$ there exists some $\epsilon_{sec} = \ngl(n)$ such that $(\gen, \rep)$ is $(q, \epsilon_{sec}, s_{sec}, f_2,..., f_q)$-reusable fuzzy extractor.
\end{theorem}
\begin{proof}
The only modification to the outline presented in \secref{ssec:sec cons sampling} is in \lemref{lem:samp unguess} with the other keys $R_1,..., R_{i-1}, R_{i+1}, ..., R_q$ treated as additional auxiliary input to the adversary/simulator.  The simulator in the definition of composable obfuscation is required to function for arbitrary circuits in the family even if the choice of these circuits depends on the previous obfuscations.  Thus allows reading $w_i$ to be chosen depending on public values $p_1,..., p_{i-1}$.
\bnote{say more here?}
\end{proof}

\subsection{More errors than entropy?}
In this section, we show when \consref{cons:sampling} supports partial block sources with more errors than entropy.  The structure of the partial block source implies that $\Hoo(W) \ge \alpha (\gamma-\beta ) = \Theta(\gamma)$.  We assume that $\Hoo(W) = \Theta(\gamma)$.  We are able to correct $o(\gamma)$ errors.
This yields:
\[
\text{\# Errors} - \text{Entropy} =  \log |B_t| -\Hoo(W) \ge t \log |\mathcal{Z}| - \Theta(\gamma)= o(\gamma) \log |\mathcal{Z}| - \Theta(\gamma)
\]
That is, there exists a super-constant alphabet size for which \consref{cons:sampling} is secure with more errors than entropy.

\textbf{Notes:} \consref{cons:sampling} works for an arbitrary size alphabet; however, for a constant size alphabet, the required entropy is greater than the number of corrected error patterns.  However, \consref{cons:sampling} is reusability for an arbitrary size alphabet.

In the analysis of \consref{cons:sampling} we restricted our attention to partial block sources, to allow for an easy comparison with \consref{cons:info theoretic}.  However,  in fact \consref{cons:sampling}  is secure for any source where sampling produces a high entropy string~(entropy $\omega(\log n)$) with overwhelming probability. For example, it is secure for sources with symbols that are $\omega(\log n)/\log |\mathcal{Z}|$-wise independent.

\section{Allowing Correlated Symbols}
\label{sec:cor construction}
In the previous two sections, we presented constructions that supported restricted classes of distributions with more errors than entropy.  Unfortunately, both Constructions~\ref{cons:info theoretic} and \ref{cons:sampling} required each symbol to contribute ``fresh'' entropy.  In this section, we present a computational construction that allows for correlation between symbols while still supporting more errors than entropy and correcting a constant fraction of errors.
This construction is inspired by the construction of digital lockers from point obfuscation by Canetti and Dakdouk~\cite{canetti2008obfuscating}.  Instead of having large parts of the string $w$ unlock $r$, we have individual symbols unlock bits of the output.
